Title Goes Here

### 2020-04-10 analysis/paper/paper.Rmd
editing the text

```{r}
# CTRL + OPTION + i to insert a code block
library(here)
SAA16 <- readxl::read_excel(here("analysis/data/SAA2016.xlsx"))
SAA17 <- readxl::read_excel(here("analysis/data/SAA2017.xlsx"))
SAA18 <- readxl::read_excel(here("analysis/data/SAA2018-finalprogram.xlsx"))
SAA19 <- readxl::read_excel(here("analysis/data/SAA2019.xlsx"))
EAA18 <- readxl::read_excel(here("analysis/data/2018 EAA.xlsx"))
CAA18 <- readxl::read_excel(here("analysis/data/2018 CAA.xlsx"))
SAA18_top_term_plot <- readRDS(here("analysis/data/SAA18 top term plot"))

@@

We are also interested in whether there is a variation in topic choices between the two biological genders in archaeological conferences. To do this we have used the process of topic modeling, which is used to find natural groups of words when we do not have a specific criteria or simply unsure what we are looking for. There are many ways to accomplish topic modeling, we have used the method of Latent Dirichlet allocation (LDA). This method is beneficial in our case because LDA does not treat one topic, which consists of many words, as separate from another topic. Before we can start using LDA, we have to first decide on the number of topics in our collection of texts. To do this we have used the R package ldatuning (add citation), which allows us to use multiple methods to compute an optimal number of groups for LDA processing. We then create a topic model for all our texts, this will assign all words in every document into topics, and assign each word a probability based on its per-topic-per-word probability, which we call beta. After this we keep only the top 10 words within each topic as keywords to represent each topic. Below is an example of a plot for the 2018 SAA that shows the predetermined number of groups each with top ten keywords in each group. From this we then have top terms from the topics of all conferences. We are only interested in keywords that are meaningful in a topic, therefore we have excluded words that are common in the field of archaeology or simply meaningless, for example, the, a, el, al, archaeology...etc. After figuring out the top terms, we can combine them with our earlier exploration of gender to see if one gender seems to favor another, for example if female or male favor topics about 'rock'.

```{r}
SAA18_top_term_plot
```

>>>>

```{r}
# CTRL + OPTION + i to insert a code block
library(here)
# column names should be:
# session, FirstName, AbstractTitle
SAA16 <- readxl::read_excel(here("analysis/data/SAA2016.xlsx"))
SAA17 <- readxl::read_excel(here("analysis/data/SAA2017.xlsx"))
SAA18 <- readxl::read_excel(here("analysis/data/SAA2018-finalprogram.xlsx"))
SAA19 <- readxl::read_excel(here("analysis/data/SAA2019.xlsx"))

EAA18 <- readxl::read_excel(here("analysis/data/2018 EAA.xlsx"))
CAA18 <- readxl::read_excel(here("analysis/data/2018 CAA.xlsx"))

@@

We are also interested in whether there is a variation in topic choices between these two genders in archaeological conferences. To do this we have used topic modeling, which is a method to automatically find related groups of words that resemble 'themes' or 'topics'. We used Latent Dirichlet allocation (LDA) because LDA does not treat one topic, which consists of many words, as separate from another topic. That is, a word can be present in many topics but with differnt weightings. When using LDA, we have to first decide on the number of topics that the method will identify in our texts. We used the R package ldatuning [citation] to compute an optimal number of topics for the LDA method to identify. We then create a topic model for all our texts, this will assign all words in every document into our set number of topics, and assign each word a probability based on its per-topic-per-word probability. To visualise the topic model we use the top 10 words within each topic as keywords to represent each topic. We excluded words that are common in the field of archaeology or have little semantic value, for example, 'the', 'a', 'el', 'al', 'archaeology', etc. We generated one topic model per conference. Each presentation at each conference is then assigned a vector of topic probabilities.

To explore the relationship between gender and topics we identified the most prominent topic for each presentation...
